---
title: "Chicken Feed"
author: "Harun Muhammad"
date: "3/07/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
```

##  Chicken feed study  

data set has chicken weights and 4 variables:
  1.  chicken weight  
  2.  chicken feed type  
  3.  chicken time in the 40" run  
  4.  chicken sex   

Idea is to determine which of the variables affect chicken weight 
The weight and time to run are numerical variables, gender and feed type are categorical variables

So we'll use templatesRMD Cat Numerical, look for the section that has an 'aov'

<!-- This question is like a bunch of t-tests, but instead of doing the t-test a bunch of times we use ANOVA to do all the comparisons at once!  !-->

### get the data

```{r}
chickenData = read.csv('chickens.csv')
head(chickenData)
attach(chickenData)
```

### Graphical summary

<!-- plot chicken weight against each of the three explanatory variables.  Weight against a categorial varable is a boxplot, weight against a numerical variable is a scatter plot !-->

boxplot of weight based on feed 

```{r}
plot(weight~feed,data=chickenData)
```
  
  It appears that the feed type has an effect.  Sunflower the best?

```{r}
plot(weight~speed,data=chickenData)
```

##Now with ggplot - first select the basic data

```{r}
basicNN <- ggplot(chickenData,aes(x=weight,y=speed))
```
##Now add in scatterplot

```{r}
basicNN + geom_point() + geom_smooth(method = "lm")
```


There does not appear to be any relationship between speed and weight



 
### Numerical summary

```{r}
summary(chickenData)
```
This is a summary of all the data in chickenData
 

### Inference -- Analysis of Variance

```{r}
model1 = lm(weight~feed+speed+sex, data=chickenData)
anova(model1)
```

this ANOVA says only feed affects chicken weight


###  Conclusions  -- which variables affect chicken weight?

Here is my brilliant conclusion

## Added by Dr K

```{r}
model2 = aov(weight~feed, data=chickenData)
anova(model2)
```

```{r}

summary.aov(model2)
```
```{r}
#we specify the margins starting at the bottom and proceeding clockwise - thus 8.7 is the left side margin to hold the names of the factors
par(mar = c(3, 8.7, 2, 2))
plot(TukeyHSD(model2),las=2)
```
